|

### 2022-07-01 manuscript/manuscript_1.0.Rmd
New plots and edits in the manuscript

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Olof Leimar^[Department of Zoology, Stockholm University, Stockholm, Sweden]
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes:
- \usepackage{float}
- \usepackage{setspace}\doublespacing
- \linespread{2}
- \usepackage{lineno}
- \linenumbers
- \floatplacement{figure}{H}
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: | 
  Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE)
require(png)
require(here)
source(here("../R_files/posPlots.r"))
source(here("AccFunc.r"))
```

@@

The outcome of interactions with con-specifics is an important 
determinant of fitness in social animals. Irrespective of whether 
such interactions are cooperative or competitive, the actions of 
interacting individuals partly determine 
their reproductive success. However, the best action for an individual 
might vary depending on its condition, and that of individuals with 
whom it interacts. Thus, acting based on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
Acquiring this information, however, is far from trivial. 
In some cases, interacting partners (signallers) might be 'willing' to 
provide accurate information, but in others it might be in their 
own interest to conceal information [@johnstone_Recognition_1997], 
or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will benefit 
from broadcasting accurate information, whereas others will benefit 
from hiding it. Take, for instance, an interaction between two individuals 
where one can help the other. Given some costs and benefits, 
a potential donor will be interested in helping 
related individuals. Therefore, for a relative of the donor, 
broadcasting kinship is advantageous, whereas for an unrelated individual, 
concealing the lack of kinship is better. Similar scenarios may apply to 
many aspects of social life such as finding mates, 
feeding offspring, dominance relationships and aggressive interactions 
[@bradbury_Principles_2011; @moller_Female_1988; @tibbetts_Socially_2004].
In dominance and aggressive interactions, an important piece of
information to guide individual actions is interacting 
partners fighting ability, which is sometimes referred to as 
Resource Holding Potential (RHP) 
[@parker_Assessment_1974], or simply as quality. 
Responsiveness to the quality of the partner is central 
to communication systems such as badges of status, 
where an arbitrary signal conveys quality 
[@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Here, arbitrary refers to a signal which is not 
ontogenetically correlated with quality. 
Badges of status can be evolutionarily stable whenever the 
signal imposes a fitness cost which decreases with the 
quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993], 
such that it's no longer in the interest of low quality individuals 
to fake quality by producing a large badge. The cost of honest signals 
is a more general principle of communications systems, 
usually referred to as the handicap principle 
[@grafen_Biological_1990; @zahavi_Mate_1975]. 
<!-- should this last part of the paragraph stay ?-->
An alternative system of communication is one where individuals 
gather and store information about each individual they interact with. 
This information should reliably allow each individual to react adaptively 
to the quality difference with their opponent. This type of 
assessment strategy is often referred to as individual 
recognition [@whitfield_Plumage_1986]. Evidently, individual recognition 
is restricted to  certain interaction structures, because individuals 
are limited by cognitive abilities in how many individuals 
they can recognize and track. Thus, individual recognition and 
badges of status have been assumed to be alternative communication 
systems fulfilling the same function, reducing the costs of 
aggression in contests over resources.

Furthermore, badges of status and individual recognition are expected 
to evolve under different interaction structures, badges of status under 
global interactions and individual recognition
under local interactions [@dale_Signaling_2001; @sheehan_There_2016].  
There is no clear cut reason, however, why both systems could not 
work together, in fact there is some evidence
that they can [@chaine_Manipulating_2018].

A somewhat ignored component of communication systems, in the context 
of aggressive interactions, is the cognitive aspects of the receiver module. 
Communication systems relying on badges of status are often assumed 
to be cognitively less demanding than those involving individual 
recognition [@sheehan_There_2016] because in the latter, 
individuals need to store identity and associated information 
about each individual they interact with. In contrast, the response 
towards badges of status is often 
thought to be innate [@botero_Evolution_2010; @johnstone_Badges_1993], with 
individuals using their own quality and the opponent's badge to determine 
whether to aggressively engage in contest. An alternative view of 
badges of status is that individuals learn 
to react to them based on their experiences [@guilford_Receiver_1991], 
which would imply that receivers must learn to associate signals with 
the fighting ability of bearers just as in systems based on individual 
recognition. In cases where badges of status vary quantitatively 
(e.g. in size or intensity), fighting ability may increase monotonically 
with attributes of the badge and would be reinforced by every interaction, 
so in principle learning would be faster than in systems involving individual 
recognition in which the association between signals and their meaning would 
vary depending on the interacting partners. In any case, learning could be 
a central cognitive mechanism in both types of communication systems, 
but the role of learning in these contexts has not been thoroughly 
explored in the empirical nor theoretical literature.

Associative learning is a key cognitive mechanism that allows 
individuals to associate rewards with environmental stimuli 
and thus behave adaptively [@staddon_Adaptive_2016]. Associative 
learning exists in all major vertebrate taxa, and in many invertebrates [@heyes_Simple_2012;@macphail_Brain_1982; @staddon_Adaptive_2016; 
@behrens_Associative_2008].
Theory has shown that natural selection favours these associations 
in complex environments where conditions are hard to predict 
[@dridi_Environmental_2016]. Besides its wide taxonomic and
ecological relevance, associative learning is a flexible cognitive 
mechanism whose underpinnings show interspecific variation [@enquist_Power_2016; @quinones_Reinforcement_2019], so presumably, it has been modified 
by natural selection. Despite all this, associative learning is 
not often included in the narrative of evolutionary explanations of 
behavioural patterns [@fawcett_Exposing_2013; @kamil_Optimal_1983; 
@mcauliffe_Psychology_2015]. Computational models of evolution 
can play an important role to overcome the lack of integration 
between learning and evolution. Reinforcement learning theory 
encompasses a series of computational methods inspired 
on the psychological and neurological mechanisms of associative learning [@sutton_Reinforcement_2018]. These set of algorithms allow the 
implementation of biologically realistic problems, 
capturing the essence of learning processes [@frankenhuis_Enriching_2018; @quinones_Reinforcement_2019]. 
Furthermore, these algorithms can be embedded in evolutionary simulations to 
generate theoretical predictions of the effect that learning can 
have in behavioural evolution [@leimar_Learning_2019].

In here we present an evolutionary model where individuals use 
associative learning to develop a tendency to behave aggressively 
(or  peacefully), in the context of competition over resources, 
depending on the quantitative morphological trait they 
perceive in their opponent (badge). Over evolutionary time 
individuals evolve the size of their badge, and whether it depends 
on their quality. Under this simple
set up, individuals can use the badge both as a signal of quality (BS)
or as a trait for IR. We use the model to assess under what conditions 
of interaction structure we expect different communication signals to evolve.

@@

We model the evolution of signals of quality in the context of agonistic 
interactions. For simplicity we consider a population of haploid 
individuals with non-overlapping generations. Individuals are born 
every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, 
which is drawnfrom a truncated normal distribution 
$N(\mu = 0.5,\sigma)$. An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of 
development processes individuals produce a morphological signal (badge), 
the size of such depends on their level 
of quality according to a reaction norm given by 
$B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$; where are $\alpha_i$ and 
$\beta_i$ are individual specific traits that determine the shape of 
the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ 
and $\beta_i$ means individuals can have either uninformative (flat) or 
informative (logistic) norms. The size of the signal is constrained 
between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value 
of the offspring. After birth individuals go through a round of 
viability selection. Individual specific survival probability is given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. Where $k_1$ and $k_2$ are parameter 
values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, 
while if $k_2>0$ lower quality individuals pay a higher price for similar-sized 
badge, fulfilling the core assumption of the handicap principle 
[@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

@@

extSimsDir<-paste0("M:/BadgeSims/",scenario1,"_")
listTest<-list.files(extSimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

extSimsDir<-paste0("M:/BadgeSims/",scenario2,"_")
listTest<-list.files(extSimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

When we allow the evolution of the sender code ($\alpha$ and $\beta$ 
change subject to natural selection and genetic drift), and the badge 
size work as a handicap (i.e. the cost of the badge is inversely 
proportional to the quality of the individual), the sender code evolves 
to produce an honest signal Fig \ref{fig:handicap}). The evolution of 
the sender code does not happen immediately after the start of the 
evolutionary process. Instead, the evolutionary dynamics of the reaction 
norm parameters (Fig. \ref{fig:handicap}, X) show a set of 
steps. First, the intercept of the reaction norm ($\alpha$) evolves to 
higher values, reducing the average badge size in the populations. 
That makes sense because reaction norms segregating in the population are 
flat at this point, and consequently the receiver code does not respond to 
the badge size, bigger badges are costlier and do not trigger lower attack 
probabilities. During those first generations, the slope of the sender 
reaction norm ($\beta$)  remains around the initial value of zero. 
At around generation 4000, the slope evolves toward positive values. 
Which implies that larger badges correlate with higher quality. Receivers 
learn to react to such correlation, reducing the probability of attack towards 
individual of larger badges. Hence, natural selection favours larger 
values of $\beta$, eventually leading to an evolutionary equilibrium where 
badge size is an honest signal of quality mediated by the learned responses 
of receivers. The evolutionary trajectory portrayed in figure 
\ref{fig:handicap} is not the only possible trajectory. If the slope of the 
sender reaction norms ($\beta$) evolves toward negative values before badges 
become handicaps, receivers never learn to react to the size of badges. 
Thus, badges are only costly and do not provide information about the 
quality of an individual. Eventually, the badge disappears from the population.

@@

>>>>

---
title: |
  | Learning can mediate both badges of status and individual recognition
author:
- Andrés E. Quiñones^[Laboratorio de Biología Evolutiva de Vertebrados, Departamento
  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia]
- C. Daniel Cadena*
- Redouan Bshary^[Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland]
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
fontsize: 12pt
header-includes: |
  ```{=latex}
    \usepackage{float}
    \usepackage{setspace}\doublespacing
    \usepackage[backref=page]{hyperref}
    \linespread{2}
    \usepackage{lineno}
    \linenumbers
    \floatplacement{figure}{H}
   \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  ```
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: | 
  Adaptive behavioural responses often depend on qualities of the interacting partner of an individual. For example, when competing for resources, an individual might be better off escalating fights with individuals of lower quality, while restraining from fighting individuals of higher quality. Communication systems involving signals of quality allow individuals to reduce uncertainty regarding the fighting ability of their partners and make more adaptive behavioral decisions. However, dishonest individuals can destabilize such communications systems. One open question is whether cognitive mechanisms, such as learning, can maintain the honesty of signals, thus, favoring their evolutionary stability. Here we present evolutionary simulations, where individuals can produce a signal proportional to their quality; and learn along their lifetime the best response to the signal emitted by their peers. In these simulations, learning on the receiver side can mediate the evolution of signals of quality on the sender side. When the cost of the signal is proportional to the quality of the sender populations are only composed of honest signalers. When the cost is not proportional to the quality of the signaler, the population is composed of both honest and dishonest signalers. We argue that learning can be a general cognitive mechanism playing a role in a wide range of communication systems.  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE,warnings=FALSE)
require(png)
require(here)
source(here("../R_files/posPlots.r"))
source(here("AccFunc.r"))
```

@@

The outcome of interactions with con-specifics is an important 
determinant of fitness in social animals. Irrespective of whether 
such interactions are cooperative or competitive, the actions of 
interacting individuals partly determine 
their reproductive success. However, the best action for an individual 
might vary depending on its condition, and that of individuals with 
whom it interacts. Thus, acting based on information about interacting 
partners is typically adaptive [@quinones_Negotiation_2016].
Acquiring this information, however, is far from trivial. 
In some cases, interacting partners (signallers) might be 'willing' to 
provide accurate information, but in others it might be in their 
own interest to conceal information [@johnstone_Recognition_1997], 
or to provide erroneous information [@johnstone_Badges_1993]. 
Typically, in a given context, some proportion of individuals will benefit 
from broadcasting accurate information, whereas others will benefit 
from hiding it. Take, for instance, an interaction between two individuals 
where one can help the other. Given some costs and benefits, 
a potential donor will be interested in helping 
related individuals. Therefore, for a relative of the donor, 
broadcasting kinship is advantageous, whereas for an unrelated individual, 
concealing the lack of kinship is better. Similar scenarios may apply to 
many aspects of social life such as finding mates, 
feeding offspring, dominance relationships and aggressive interactions 
[@bradbury_Principles_2011; @moller_Female_1988; @tibbetts_Socially_2004].
In dominance and aggressive interactions, an important piece of
information to guide individual actions is interacting 
partners fighting ability, which is sometimes referred to as 
Resource Holding Potential (RHP) 
[@parker_Assessment_1974], or simply as quality. 
Responsiveness to the quality of the partner is central 
to communication systems such as badges of status, 
where an arbitrary signal conveys quality 
[@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Here, arbitrary refers to a signal which is not 
ontogenetically correlated with quality. 
Badges of status can be evolutionarily stable whenever the 
signal imposes a fitness cost which decreases with the 
quality of an individual  [@botero_Evolution_2010; @johnstone_Badges_1993], 
such that it's no longer in the interest of low quality individuals 
to fake quality by producing a large badge. The cost of honest signals 
is a more general principle of communications systems, 
usually referred to as the handicap principle 
[@grafen_Biological_1990; @zahavi_Mate_1975]. 
<!-- should this last part of the paragraph stay ?-->
<!-- An alternative system of communication is one where individuals  -->
<!-- gather and store information about each individual they interact with.  -->
<!-- This information should reliably allow each individual to react adaptively  -->
<!-- to the quality difference with their opponent. This type of  -->
<!-- assessment strategy is often referred to as individual  -->
<!-- recognition [@whitfield_Plumage_1986]. Evidently, individual recognition  -->
<!-- is restricted to  certain interaction structures, because individuals  -->
<!-- are limited by cognitive abilities in how many individuals  -->
<!-- they can recognize and track. Thus, individual recognition and  -->
<!-- badges of status have been assumed to be alternative communication  -->
<!-- systems fulfilling the same function, reducing the costs of  -->
<!-- aggression in contests over resources.  -->

<!-- Furthermore, badges of status and individual recognition are expected  -->
<!-- to evolve under different interaction structures, badges of status under  -->
<!-- global interactions and individual recognition -->
<!-- under local interactions [@dale_Signaling_2001; @sheehan_There_2016].   -->
<!-- There is no clear cut reason, however, why both systems could not  -->
<!-- work together, in fact there is some evidence -->
<!-- that they can [@chaine_Manipulating_2018]. -->

A somewhat ignored component of communication systems, in the context 
of aggressive interactions, is the cognitive aspects of the receiver module. 
Theoretical models often assume that Communication systems relying on badges of 
status to have reaction norms as their 
mechanistic underpinning [@Botero_Evolution_2010], with 
individuals using their own quality and the opponent's badge to determine 
whether to aggressively engage in contest. Reaction norms 
allow individuals to respond to the available information without a big
cognitive burden. That is at least in contrast to other information processing 
mechanisms like individual recognition. With individual recognition 
individuals associate cue of their peers to their quality. These association 
must be learn thoughout individuals lifes, thus it has the usual 
cognitive requirements of an associative learning process. An alternative view 
of badges of status is that individuals learn 
to react to them based on their experiences [@guilford_Receiver_1991], 
which would imply that receivers must learn to associate signals with 
the fighting ability of bearers just as in systems based on individual 
recognition. In cases where badges of status vary quantitatively 
(e.g. in size or intensity), fighting ability may increase monotonically 
with attributes of the badge and would be reinforced by every interaction, 
so in principle learning would be faster than in systems involving individual 
recognition in which the association between signals and their meaning would 
vary depending on the interacting partners. In any case, learning could be 
a central cognitive mechanism in both types of communication systems, 
but the role of learning in these contexts has not been thoroughly 
explored in the empirical nor theoretical literature.

Associative learning is a key cognitive mechanism that allows 
individuals to associate rewards with environmental stimuli 
and thus behave adaptively [@staddon_Adaptive_2016]. Associative 
learning exists in all major vertebrate taxa, and in many invertebrates
as well [@heyes_Simple_2012;@macphail_Brain_1982; @staddon_Adaptive_2016; 
@behrens_Associative_2008].
Theory has shown that natural selection favours these associations 
in complex environments where conditions are hard to predict 
[@dridi_Environmental_2016]. Besides its wide taxonomic and
ecological relevance, associative learning is a flexible cognitive 
mechanism whose underpinnings show interspecific variation 
[@enquist_Power_2016; @quinones_Reinforcement_2019], so presumably, it has been modified 
by natural selection. Despite all this, associative learning is 
not often included in the narrative of evolutionary explanations of 
behavioural patterns [@fawcett_Exposing_2013; @kamil_Optimal_1983; 
@mcauliffe_Psychology_2015]. Computational models of evolution 
can play an important role to overcome the lack of integration 
between learning and evolution. Reinforcement learning theory 
encompasses a series of computational methods inspired 
on the psychological and neurological mechanisms of associative 
learning [@sutton_Reinforcement_2018]. These set of algorithms allow the 
implementation of biologically realistic problems, 
capturing the essence of learning processes 
[@frankenhuis_Enriching_2018; @quinones_Reinforcement_2019]. 
Furthermore, these algorithms can be embedded in evolutionary simulations to 
generate theoretical predictions of the effect that learning can 
have in behavioural evolution [@leimar_Learning_2019].

In here we present an evolutionary model where individuals use 
associative learning to develop a tendency to behave aggressively 
(or  peacefully), in the context of competition over resources, 
depending on the quantitative morphological trait they 
perceive in their opponent (badge). Over evolutionary time 
individuals evolve the size of their badge, and whether it depends 
on their quality. Under this simple
set up, individuals can use the badge as a signal of quality. 
We use the model to assess under what conditions 
of interaction structure we expect different communication signals to evolve.

@@

We model the evolution of signals of quality in the context of agonistic 
interactions. For simplicity we consider a population of haploid 
individuals with non-overlapping generations. Individuals are born 
every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, 
which is drawn from a truncated normal distribution 
$N(\mu = 0.5,\sigma)$. An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of 
development processes individuals produce a morphological signal (badge), 
the size of such depends on their level 
of quality according to a reaction norm given by 
$B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$; where are $\alpha_i$ and 
$\beta_i$ are individual specific traits that determine the shape of 
the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ 
and $\beta_i$ means individuals can have either uninformative (flat) or 
informative (logistic) norms. The size of the signal is constrained 
between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value 
of the offspring. After birth individuals go through a round of 
viability selection. Individual specific survival probability is 
given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. Where $k_1$ and $k_2$ are parameter 
values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, 
while if $k_2>0$ lower quality individuals pay a higher price for similar-sized 
badge, fulfilling the core assumption of the handicap principle 
[@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

@@

SimsDir<-here("Simulations",paste0(scenario1,"_"))
listTest<-list.files(SimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

SimsDir<-SimsDir<-here("Simulations",paste0(scenario2,"_"))
listTest<-list.files(SimsDir,full.names = TRUE)
indList<-grep("ind",listTest,value=TRUE)
# parameter values from project folder
paramName<-list.files(here("Simulations",paste0(scenario1,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE)
param<-fromJSON(here("Simulations",paste0(scenario1,"_"),paramName[2]))
# fromJSON(paramName[1])
fileId<-1 # choose the replicate

@@

When we allow the evolution of the sender code ($\alpha$ and $\beta$ 
change subject to natural selection and genetic drift), and the badge 
size work as a handicap (i.e. the cost of the badge is inversely 
proportional to the quality of the individual), the sender code evolves 
to produce an honest signal Fig \ref{fig:handicap}). The evolution of 
the sender code does not happen immediately after the start of the 
evolutionary process. Instead, the evolutionary dynamics of the reaction 
norm parameters (Fig. \ref{fig:handicap}, X) show a set of 
steps. First, the intercept of the reaction norm ($\alpha$) evolves to 
higher values, reducing the average badge size in the populations. 
That makes sense because reaction norms segregating in the population are 
flat at this point, and consequently the receiver code does not respond to 
the badge size, bigger badges are costlier and do not trigger lower attack 
probabilities. During those first generations, the slope of the sender 
reaction norm ($\beta$)  remains around the initial value of zero. 
At around generation 4000, the slope evolves toward positive values. 
Which implies that larger badges correlate with higher quality. Receivers 
learn to react to such correlation, reducing the probability of attack towards 
individual of larger badges. Hence, natural selection favours larger 
values of $\beta$, eventually leading to an evolutionary equilibrium where 
badge size is an honest signal of quality mediated by the learned responses 
of receivers. The evolutionary trajectory portrayed in figure 
\ref{fig:handicap} is not the only possible trajectory. If the slope of the 
sender reaction norms ($\beta$) evolves toward negative values before badges 
become handicaps, receivers never learn to react to the size of badges. 
Thus, badges are only costly and do not provide information about the 
quality of an individual(Fig. \ref{fig:noBadge} . Eventually, the badge disappears from the population.

@@

# Supplementary material

```{=tex}
\beginsupplement
```

```{r noBadge,echo=FALSE,warning=FALSE,out.width='90%',fig.align='center',fig.show='hold',fig.cap= "The evolution of cheap signals. Portrait of the evolutionary dynamics of the sender code with snapsots of both sender and receiver codes just as in fig. \\ref{fig:handicap}. The middle panels show changes in the distribution of values fir $\\alpha$ and $\\beta$ along evolutionary time. Panels above and bellow correspond to snapshots of the sender and receiver codes, respectively, generation time of the snapshots are indicated by the grey lines in the middle panels."}

knitr::include_graphics(here("Simulations","betCostEvol1_","evolDyn5_betCost5.png"))
